New Computer Fan Data-Science Set-up\\ Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)\\ Atom, VScode, Pycharm

### 2020-01-03 nontex/install/windows/fn_installations.tex
installation clean up, sumatra color pdf as VSCode latex pdf

@@

@@

  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}

@@

\usepackage{microtype}

@@

@@

\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations},

@@

@@

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{New Computer Data-Science Set-up: Python (anaconda, pycharm), R
(r-studio) and other Programs Installations}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

@@

For the following types of programming tasks, install relevant programs,
that are cross platform compatible. Test at the end that example
programs work.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Python

  \begin{itemize}
  \tightlist
  \item
    Anaconda Dist
  \item
    Pycharm
  \item
    atom hydrogen
  \end{itemize}
\item
  R

  \begin{itemize}
  \tightlist
  \item
    R
  \item
    Rstudio
  \item
    atom hydrogen
  \end{itemize}
\item
  Matlab

  \begin{itemize}
  \tightlist
  \item
    Matlab
  \end{itemize}
\item
  Latex and PDF

  \begin{itemize}
  \tightlist
  \item
    atom latex
  \item
    texstudio
  \item
    texlive
  \item
    okular pdf
  \end{itemize}
\end{enumerate}

@@

  \begin{itemize}
  \tightlist
  \item
    work from command line?
  \item
    work from atom (hydrogen)
  \end{itemize}
\item
  Do sample \emph{rmd} files work?

  \begin{itemize}
  \tightlist
  \item
    work from r-studio
  \item
    work from atom (hydrogen), r file
  \end{itemize}
\item
  Do tex templates compile?

  \begin{itemize}
  \tightlist
  \item
    tikz files
  \item
    template files with bib
  \end{itemize}
\end{enumerate}

\emph{note}: Github people seem to have slowed down updating Atom since
microsoft acquisition

\hypertarget{conda}{%
\section{Conda}\label{conda}}

@@

Search for Anaconda Prompt, right click, choose run as administrator.

Check software versions.

@@

Download and install for all users. Afterwards, Anaconda does not
automatically get added to Windows Path. Need to use Anaconda Prompt to
access programs. To access Anaconda packages from windows prompt, from
git bash, from R, etc, need to Add Anaconda to Windows Path

To install conda in Debian, follow
\href{https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html}{these
instructions}.

See Anaconda Installation Directory, in anaconda prompt:

@@

@@

\hypertarget{conda-test-python}{%
\subsection{Conda Test Python}\label{conda-test-python}}

@@

\hypertarget{jupyter-and-atom-hydrogen}{%
\subsection{Jupyter and Atom Hydrogen}\label{jupyter-and-atom-hydrogen}}

For both Jupyter as well as Atom, always open from command prompt, open
from \emph{Anaconda Prompt} with admin rights.

First, open up \emph{Jupyter Notebook}, does the python kernel work? If
does not, uninstall and re-install Anaconda.

Now test python within atom:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  install hydrogen in atom. Follow
  \href{http://nteract.io/atom}{instructions}.

  \begin{itemize}
  \tightlist
  \item
    terminal in windows or linux after installation: \emph{apm install
    hydrogen}
  \item
    apm is the atom package manager.
  \end{itemize}
\item
  Pull/Sync with Git and open mulitple projects in atom, follow
  \href{https://fanwangecon.github.io/Tex4Econ/nontex/install/git/fs_git_setup.html}{guide
  here}.
\item
  go to the programs above and try to run.
\end{enumerate}

\CommentTok{# Inside Conda open up atom}
\ExtensionTok{atom}

\CommentTok{# open multiple projects from atom at the same time, after repos synced}
\ExtensionTok{atom}\NormalTok{ ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ}
\CommentTok{# open up any py from from within, try 1+1, does it work?}
\CommentTok{# also use script, try ctrl + shift + b, run whole file (not hydrogen)}
\end{Highlighting}
\end{Shaded}

@@

Try to install R from within Conda. The procedure here is the same for
windows as well as linux machines.

@@

Open up RStudio, and see where paths are. also open up R from command
prompt, see where paths are.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{.libPath}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

Open up install and uninstall programs, find R and Rstudio, and
uninstall them. Then delete all files found path paths shown by
\emph{.libPath()}, looking at these: -
\emph{C:/Users/fan/Documents/R/win-library/3.6} - \emph{C:/Program
Files/R/R-3.6.1/library}

\begin{itemize}
\tightlist
\item
  if used apt-get to install, R installed under main user drive,
  deactivate conda, and check which conda
\end{itemize}

@@

@@

  \begin{itemize}
  \tightlist
  \item
    for debian:
    \href{https://cran.r-project.org/bin/linux/debian/}{Johannes Ranke}
  \end{itemize}
\item
  \href{https://rstudio.com/products/rstudio/download/}{download
  R-studio}
\item
  Open R-studio and auto-detect R
\item
  Install packages
\end{enumerate}

note that installation will not work if the machine's version of R is
not up to date, this could be the case with default R versions for some
linux installations. For Debian for example, need to update the
\emph{source.list} to include sources that have more recent versions of
R.

Additionally, need to install \emph{libcurl4-openssl-dev} and
\emph{libssl-dev} from command prompt first inside Debian.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# If inside Debian, due to some tidymodel install issues, do this`}
\ExtensionTok{conda}\NormalTok{ install -c r r}
\ExtensionTok{conda}\NormalTok{ install -c r r-essentials}
\ExtensionTok{conda}\NormalTok{ install -c r r-igraph}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge igraph}

\CommentTok{# Go to get latesdebian latest r sources.list}
\FunctionTok{cat}\NormalTok{ /etc/apt/sources.list}
\CommentTok{# Install this First (should already be installed)}
\FunctionTok{sudo}\NormalTok{ apt install dirmngr}

@@

Which R?

@@

\hypertarget{set-up-r-environment-in-conda}{%
\subsection{Set up R-Environment in
Conda}\label{set-up-r-environment-in-conda}}

Conda environments are language agnostic. pip is a package manager for
Python. venv is an environment manager for Python. conda is both a
package and environment manager and is language agnostic. Inside
Anaconda Prompt:

Key packages are generally available in conda's default channel
(official distribution) and also the more frequently updated conda-forge
channel. Prioritize conda-forge to get the latest packages. after adding
\emph{conda-forge} to channels, that will be prioritized, so when
creating a new environment, conda will install first from conda-forge if
package exists there. Try the \emph{r\_env} generation line with and
without first adding \emph{conda-forge} to channel, and see that the
packages installed will have different versions, reflecting versions in
the default channel and in the \emph{conda-forge} channels.

@@

\CommentTok{# install files}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y}

\CommentTok{# trouble with igraph installation, install here from conda}
\CommentTok{# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-igraph}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c conda-forge igraph}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-rstantools r-rstan r-rstanarm -y}

@@

\hypertarget{install-additional-packages-inside-the-r-environment}{%
\subsection{Install Additional Packages inside the
R-environment}\label{install-additional-packages-inside-the-r-environment}}

These are packages that I use, these should be installed inside the
environment. Or they could be installed later from inside r-studio.
Installing inside r-studio is a lot better.

\emph{tidymodel} has installation issues sometimes.

In \emph{r\_env}, type in \emph{R}, and then install from inside
terminal's R:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# enter into env}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\CommentTok{# enter R or type in rstudio}
\CommentTok{# sicne R is only install inside r_env, has to enter rstudio from r_env}
\ExtensionTok{R}
\ExtensionTok{rstudio}

\CommentTok{# main packagevps}
\CommentTok{# tidymodel installation on linux difficult}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"rstantools"}\NormalTok{, }\StringTok{"rstan"}\NormalTok{, }\StringTok{"rstanarm"}\NormalTok{))}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}

\CommentTok{# tidymodels}
\CommentTok{# development packages}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
\CommentTok{# other packages}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

\CommentTok{# Install my package, need to prepare package to work for ubuntu}
\CommentTok{# if install does not work, load locally}
\ExtensionTok{devtools}\NormalTok{::install_github(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}

\CommentTok{# Kernel}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
\FunctionTok{IRkernel::installspec()}
\end{Highlighting}
\end{Shaded}

Install additional packages from inside R. The devtools install will
install packages inside \emph{envs/r\_env/Lib/R}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#######################################}
\CommentTok{### Own Package}
\CommentTok{#######################################}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
\CommentTok{# install_dev("cli")}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{install-packages-from-r-studio}{%
\subsection{Install Packages from
R-Studio}\label{install-packages-from-r-studio}}

Install addition files inside Rstudio. Easier to debug potentially.
Install rtools as described
\href{https://thecoatlessprofessor.com/programming/cpp/installing-rtools-for-compiled-code-via-rcpp/}{here}:
\href{https://cran.r-project.org/bin/windows/Rtools/}{rtools download}.
Alternatively:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\CommentTok{# Note that this will generate several pop-up windows}
\KeywordTok{install.Rtools}\NormalTok{()}
\CommentTok{# choose to only install 64 bit toolchain}
\CommentTok{# this installs g++ which is needed for rstanarm}
\CommentTok{# Add these below to windows path}
\CommentTok{# c:/Rtools/bin;}
\CommentTok{# c:/Rtools/mingw_64/bin;}

\ControlFlowTok{if}\NormalTok{ (}\OperatorTok{!}\KeywordTok{require}\NormalTok{(devtools)) \{}
  \KeywordTok{install.packages}\NormalTok{(}\StringTok{"devtools"}\NormalTok{)}
  \KeywordTok{library}\NormalTok{(devtools)}
\NormalTok{\}}
\KeywordTok{library}\NormalTok{(devtools)}
\KeywordTok{install_github}\NormalTok{(}\StringTok{"stan-dev/rstanarm"}\NormalTok{, }\DataTypeTok{args =} \StringTok{"--preclean"}\NormalTok{)}

\KeywordTok{setwd}\NormalTok{(}\StringTok{'C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library'}\NormalTok{)}

\KeywordTok{install.packages}\NormalTok{(}\StringTok{"stan-dev/rstanarm"}\NormalTok{, }\DataTypeTok{dependencies=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{INSTALL_opts =} \KeywordTok{c}\NormalTok{(}\StringTok{'--no-lock'}\NormalTok{))}

\CommentTok{# other packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidymodels"}\NormalTok{, }\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

\CommentTok{# for r-kernel to work in Atom}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{'IRkernel/IRkernel'}\NormalTok{)}
\NormalTok{IRkernel}\OperatorTok{::}\KeywordTok{installspec}\NormalTok{()}

\CommentTok{# Install my package}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{test-files}{%
\subsubsection{Test Files}\label{test-files}}

@@

\hypertarget{install-latex}{%
\section{Install Latex}\label{install-latex}}

@@

\hypertarget{compile-in-atom-and-texstudio}{%
\subsection{Compile in Atom and
Texstudio}\label{compile-in-atom-and-texstudio}}

@@

Go to Tex4Econ and compile various template files and other types of
files there to see if tex is working.

Compile the same files in texstudio.

\hypertarget{editors}{%
\subsection{Editors}\label{editors}}

In addition to Atom, which is pretty slow, and harder to run on lower
spec computers.

\hypertarget{vscode}{%
\subsubsection{VSCode}\label{vscode}}

VSCode is much more light-weight than Atom, does not have hydrogen.

\CommentTok{# Change Font (https://www.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)}
\CommentTok{# modify: /usr/share/applications/code.desktop}
\ExtensionTok{nvim}\NormalTok{ /usr/share/applications/code.desktop}
\CommentTok{#replace this line: Exec=/usr/share/code/code --unity-launch %F}
\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--unity-launch %F"}
\CommentTok{#replace this line: Exec=/usr/share/code/code --new-window %F}
\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--new-window %F"}

Extensions to Download for VSCode:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \href{https://marketplace.visualstudio.com/items?itemName=ms-python.python}{Microsoft
  Python Extension}
\end{enumerate}

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%

@@

  \usepackage{textcomp} % provides euro and other symbols

@@

  \usepackage{unicode-math}

@@

\usepackage[]{microtype}

@@

\usepackage{xcolor}

@@

\hypersetup{

@@

            filecolor=Maroon,

@@

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\title{New Computer Fan Data-Science Set-up\\
Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)\\
Atom, VScode, Pycharm}
\author{}
\date{\vspace{-2.5em}}

@@

Install various compilers and IDE:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Python (Anaconda, Pycharm + VSCode + Atom)
\item
  R (VSCode + Atom)
\item
  Matlab
\item
  Latex and PDF (texlive, Okular, VSCode + Atom + Texstudio)
\end{enumerate}

@@

  \begin{itemize}
  \tightlist
  \item
    work from command line
  \item
    work from atom (hydrogen), Pycharm, VSCode
  \end{itemize}
\item
  Do sample \emph{rmd} files work?

  \begin{itemize}
  \tightlist
  \item
    work from r-studio
  \item
    work from atom (hydrogen), VSCode
  \end{itemize}
\item
  Do tex templates compile?

  \begin{itemize}
  \tightlist
  \item
    tikz files, template files with bib
  \item
    work from texstudio, VSCode live compile, Atom
  \end{itemize}
\end{enumerate}

Installation Plan outline:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Conda install (python)
\item
  Install Atom along with Hydrogen and other packages.
\end{enumerate}

\hypertarget{python-and-anaconda-installation}{%
\section{Python and Anaconda
Installation}\label{python-and-anaconda-installation}}

@@

\begin{itemize}
\tightlist
\item
  Search for Anaconda Prompt, right click, choose run as administrator.
\item
  Check software versions.
\end{itemize}

@@

\href{https://www.anaconda.com/distribution/}{Download Anaconda Python
3} and install for all users. Afterwards, Anaconda does not
automatically get added to Windows Path. Need to use Anaconda Prompt to
access programs. To access Anaconda packages from windows prompt, from
git bash, from R, etc, need to Add Anaconda to Windows Path.

To install conda in Linux/Debian, follow
\href{https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html}{these
instructions}. Overall, installations are very similar.

In command/anaconda prompt:

@@

There are different channels/repositories from which packages could be
installed: \emph{conda}, \emph{conda-forge}, for example. Can change
where to look for packages first. Many packages are in multiple
channels. Conda-forge often have mroe recent packages.

@@

\hypertarget{python-command-line-test}{%
\subsection{Python Command Line Test}\label{python-command-line-test}}

@@

@@

R could be installed from Anaconda or directly on windows outside of the
Anaconda directories. When installing from within Anaconda, could create
R environment that are isolated from the rest of the computer. The R
environment could be updated and deleted without disturbing dependencies
in conda main or the rest of the computer.

The computer could have multiple R installations. Several in different
conda R environment, and also several under windows/linux primary main
user R directories. Type \emph{which R/where R} to see if you open up R
from command line at the moment, which directory's R will be used.
Inside Conda R environment, it will be a different R if there is a
different R version there.

@@

If R was installed in R enviornments, just delete the environment.
Otherwise, use system's uninstaller. Before that, from
terminal/command-prompt, type \emph{R}, and \emph{.libPaths()} to find
paths. Do so inside conda main, outside of conda main, inside different
environments, find all paths. After uninstaller finishes, check in the
libPath folders to see if there are still stuff there, delete all,
delete the folders.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{.libPath}\NormalTok{()}
\CommentTok{# C:/Users/fan/Documents/R/win-library/3.6}
\CommentTok{# C:/Program Files/R/R-3.6.1/library}
\end{Highlighting}
\end{Shaded}

For Linux and for unsintalling inside conda:

@@

Need to install R. Then need to install also an editor/IDE for R.
Rstudio is the dominant R IDE. VSCode and Atom also works well,
especially VSCode as editors. Dramatically better experience for writing
scripts outside of Rstudio which feels unwieldy and slow especially
compared to VSCode.

Overall plan:

@@

  \begin{itemize}
  \tightlist
  \item
    for debian:
    \href{https://cran.r-project.org/bin/linux/debian/}{Johannes Ranke}.
    For Linux/Debian installation, crucial to update the
    \emph{source.list} to include sources that have more recent versions
    of R. If not, will get very old R versions that is not compatible
    with many packages.
  \item
    add R to path for Windows. In Windows Path, add for example:
    \emph{C:/Program Files/R/R-3.6.2/bin/x64/} and \emph{C:/Rtools/bin}
  \end{itemize}
\item
  \href{https://rstudio.com/products/rstudio/download/}{download
  R-studio}
\item
  Open R-studio and auto-detect R
\item
  Install additional packages (from commandline)

  \begin{itemize}
  \tightlist
  \item
    various R data-science packages have dependencies, and additional
    not-R programs might need to be installed. Install them as needed,
    for example: \emph{libcurl4-openssl-dev} and \emph{libssl-dev} from
    command prompt first inside Debian.
  \end{itemize}
\end{enumerate}

\hypertarget{linux-r-install}{%
\subsubsection{Linux R Install}\label{linux-r-install}}

For linux/Debian, to Install latest R:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Go to get latesdebian latest r sources.list}
\FunctionTok{cat}\NormalTok{ /etc/apt/sources.list}
\CommentTok{# Install this First (should already be installed)}
\FunctionTok{sudo}\NormalTok{ apt install dirmngr}

@@

\hypertarget{install-packages-for-r}{%
\subsubsection{Install Packages for R}\label{install-packages-for-r}}

From command prompt, enter R by typeing \emph{R}, and install packages:

@@

\hypertarget{install-r-inside-conda}{%
\subsection{Install R (inside Conda)}\label{install-r-inside-conda}}

Key packages are generally available in conda's default channel
(official distribution) and also the more frequently updated conda-forge
channel. Prioritize conda-forge to get the latest packages. After adding
\emph{conda-forge} to channels, that will be prioritized, so when
creating a new environment, conda will install first from conda-forge if
package exists there. Try the \emph{r\_env} generation line with and
without first adding \emph{conda-forge} to channel, and see that the
packages installed will have different versions, reflecting versions in
the default channel and in the \emph{conda-forge} channels.

\hypertarget{set-up-conda-r-environment}{%
\subsubsection{Set up Conda R
environment}\label{set-up-conda-r-environment}}

Create a Conda Environment called \emph{r\_env}, and update its
channels.

@@

@@

\hypertarget{install-r-and-some-packages-in-conda}{%
\subsubsection{Install R and Some Packages in
Conda}\label{install-r-and-some-packages-in-conda}}

Either inside a R specific environment, or outside of it, now do
additional installations for R and also R packages.

During installation, the R programs might require downgrading other
programs in the Conda environment that Python for example also uses.
That is why potentially it is safer to install in R environment.
However, when installing in R enviornment, certain packages could have
issues if installer does not realize it is in an environment with
special folder structure, so installation could fail.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# install files}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y}

\CommentTok{# trouble with igraph installation, install here from conda}
\CommentTok{# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-igraph}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c conda-forge igraph}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-rstantools r-rstan r-rstanarm -y}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-additional-packages-inside-the-r}{%
\subsection{Install Additional Packages inside the
R}\label{install-additional-packages-inside-the-r}}

These are packages that I use, these should be installed inside the
environment. Or they could be installed later from inside r-studio.
Installing inside r-studio is a lot better. \emph{tidymodel} has
installation issues sometimes.

In \emph{r\_env}, type in \emph{R}, and then install from inside
terminal's R. For conda env, devtools will be installed and will install
packages inside \emph{envs/r\_env/Lib/R}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# enter into env}
\CommentTok{# conda activate r_env}
\CommentTok{# enter R or type in rstudio}
\CommentTok{# sicne R is only install inside r_env, has to enter rstudio from r_env}
\CommentTok{# R}
\CommentTok{# rstudio}

\CommentTok{# main packagevps}
\CommentTok{# tidymodel installation on linux difficult}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"rstantools"}\NormalTok{, }\StringTok{"rstan"}\NormalTok{, }\StringTok{"rstanarm"}\NormalTok{))}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}

\CommentTok{# tidymodels}
\CommentTok{# development packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
\CommentTok{# other packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

@@

Is RSTUDIO pointing to the R installation you want? Note you can open
Rstudio from differen conda env command line, that will use different R
installations. Or also set:

\hypertarget{r-tests}{%
\subsection{R Tests}\label{r-tests}}

@@

\hypertarget{install-latex-and-pdf}{%
\section{Install Latex and PDF}\label{install-latex-and-pdf}}

@@

Test file compilations in TexStudio.

\hypertarget{okular-pdf}{%
\subsection{Okular PDF}\label{okular-pdf}}

Linux: \emph{sudo apt-get install okular} Windows: install okular from
windows app store

\hypertarget{okular-shortcuts-and-features}{%
\subsubsection{Okular Shortcuts and
Features}\label{okular-shortcuts-and-features}}

\textbf{Features}:

\begin{itemize}
\tightlist
\item
  Okular 3 pages per row view:

  \begin{itemize}
  \tightlist
  \item
    view, overview
  \end{itemize}
\item
  Automatic Update when PDF updated elsewhere

  \begin{itemize}
  \tightlist
  \item
    this is one of the key reasons to use okular, when I knit a Rmd file
    to PDF, the currently open Okular PDF file automatically updates and
    does not give file is open error like Acrobat.
  \end{itemize}
\item
  Background color:

  \begin{itemize}
  \tightlist
  \item
    can easily change background color to non-white.
  \end{itemize}
\end{itemize}

\textbf{Shortcuts}:

\begin{itemize}
\tightlist
\item
  Okular configure shortcuts: setting, configure shortcuts
\item
  Okular if menu bar lost: \emph{Ctrl + m}
\item
  Okular comment pane: \emph{F6}
\item
  Okular close left pane: \emph{F7}
\item
  Okular full scrren: \emph{Ctrl + Shift + F}

  \begin{itemize}
  \tightlist
  \item
    unlike acrobat, pdf allows for multiple scrrens
  \end{itemize}
\end{itemize}

\hypertarget{adobe-pdf}{%
\subsection{Adobe PDF}\label{adobe-pdf}}

PDF Adobe Acrobat Installation + go to adobe website, log in using
\href{mailto:fwang26@uh.edu}{\nolinkurl{fwang26@uh.edu}} + go to my
account, choose view and download my apps, choose acrobat \& PDF,
download Acrobat DC + UH account can only be activated on two accounts
at once, so need to kick other computers out temporarily potentially

\hypertarget{install-various-editors}{%
\section{Install Various Editors}\label{install-various-editors}}

Atom, VSCode, Notepad++, Sublime, etc. These are essential editors that
allows for pleasant programming and writing experiences. See here for
\href{http://fanwangecon.github.io/}{fan} instructions on
\href{https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_vim.html}{vim}
installations.

\hypertarget{vscode-installation}{%
\subsection{VSCode Installation}\label{vscode-installation}}

VSCode is much more light-weight than Atom, much faster. On Windows,
download \href{https://code.visualstudio.com/download}{here}.

\CommentTok{# Change Font (https://wwFw.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)}
\CommentTok{# modify: /usr/share/applications/code.desktop}
\ExtensionTok{nvim}\NormalTok{ /usr/share/applications/code.desktop}
\CommentTok{#replace this line: Exec=/usr/share/code/code --unity-launch %F}
\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--unity-launch %F"}
\CommentTok{#replace this line: Exec=/usr/share/code/code --new-window %F}
\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--new-window %F"}

\hypertarget{vscode-extensions}{%
\subsubsection{VSCode Extensions}\label{vscode-extensions}}

Press \emph{Ctrl + P}, paste the \emph{ext install} commands below to
install extensions:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# [Microsoft Python Extension](https://marketplace.visualstudio.com/items?itemName=ms-python.python)}
\ExtensionTok{ext}\NormalTok{ install ms-python.python}
\CommentTok{# [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop)}
\ExtensionTok{ext}\NormalTok{ install latex-workshop}
\CommentTok{# [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r)}
\ExtensionTok{ext}\NormalTok{ install ikuyadeu.r}
\end{Highlighting}
\end{Shaded}

\hypertarget{vscode-shortcuts-and-features}{%
\subsubsection{VSCode Shortcuts and
Features}\label{vscode-shortcuts-and-features}}

\textbf{Features}:

\textbf{Shortcuts} :

\begin{itemize}
\tightlist
\item
  Zen model: \emph{Ctrl + k, z}, this means press control k, then press
  z
\item
  Open up Settings: \emph{Ctrl + ,}
\item
  Preview Markdown in VSCode: \emph{Ctrl + Shift + V}
\item
  Open up left pane: \emph{Ctrl + B}
\item
  Wrap Text: \emph{alt + Z}, switch between wrap or not to save screen
  space for example.
\end{itemize}

\hypertarget{vscode-and-r}{%
\subsubsection{VSCode and R}\label{vscode-and-r}}

  \begin{itemize}
  \tightlist
  \item
    \emph{r.rterm.linux}:
    \emph{/home/wangfanbsg75/anaconda3/envs/r\_env/bin/R}
  \item
    \emph{r.rterm.windows}: \emph{C:/Program
    Files/R/R-3.6.2/bin/x64/R.exe}

    \begin{itemize}
    \tightlist
    \item
      note \emph{R.exe} at the end
    \end{itemize}
  \end{itemize}
\item
  Run:

Download
\href{https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop}{Latex
Workshop}.

\hypertarget{atom-installation}{%
\subsection{Atom Installation}\label{atom-installation}}

Atom is slow but has clean look and nice git/github integration.

\hypertarget{atom-extensions}{%
\subsubsection{Atom Extensions}\label{atom-extensions}}

Terminal in windows or linux after installation: \emph{apm install
hydrogen}. apm is the atom package manager:

\CommentTok{# Inside Conda open up atom}
\ExtensionTok{atom}
\end{Highlighting}
\end{Shaded}

\hypertarget{atom-shortcuts-and-features}{%
\subsubsection{Atom Shortcuts and
Features}\label{atom-shortcuts-and-features}}

\textbf{Features}:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# open multiple projects from atom at the same time, after repos synced}
\ExtensionTok{atom}\NormalTok{ ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ}
\CommentTok{# open up any py from from within, try 1+1, does it work?}
\CommentTok{# also use script, try ctrl + shift + b, run whole file (not hydrogen)}
\end{Highlighting}
\end{Shaded}

\textbf{Shortcuts} :

\begin{itemize}
\tightlist
\item
  Git Pane: \emph{Ctrl + 9}, \emph{Ctrl + 8}
\end{itemize}

\hypertarget{atom-and-python}{%
\subsubsection{Atom and Python}\label{atom-and-python}}

Having installed Anaconda, now install Atom and Hydrogen to Test with
Python. For both Jupyter as well as Atom, always open from command
prompt, open from \emph{Anaconda Prompt} with admin rights.

Open up \emph{Jupyter Notebook}, does the python kernel work? If does
not, uninstall and re-install Anaconda.

Try \emph{1+1}.

\hypertarget{atom-and-latex}{%
\subsubsection{Atom and Latex}\label{atom-and-latex}}

@@

\hypertarget{other-editors}{%
\subsection{Other Editors}\label{other-editors}}
